Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
little tweaks to experiment flow section

After explaining the situation and their role, we will explain what Tor is, and how they can use it if necessary, and instruct them to complete the a set of tasks which will require visiting blocked websites. Ultimately, the participants will need to configure their Tor Browser to circumvent the simulated censorship environment. These tasks have a three-fold purpose of providing participants with feedback (if they did not correctly configure their browser, they cannot reach the website),  motivating the participants to configure the browser correctly, and providing the researchers with an indicator of successful censorship circumvention.

We will end the experiment with a survey that 1) measures participant demographics, participant technical fluency, and participant familiarity with Tor and 2) collects qualitative feedback on from participants on their browsing experience, particularly with respect to any parts of the configuration interface which was confusing to them, but also about the browsing experience as a whole.  A rough draft of the survey can be found \href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.\\

>>>>

After explaining the situation and their role, we will explain what Tor is, and how they can use it if necessary, and instruct them to complete the a set of tasks which will require visiting blocked websites. Ultimately, the participants will need to configure their Tor Browser to circumvent the simulated censorship environment. These tasks have a three-fold purpose of providing participants with feedback (if they did not correctly configure their browser, they cannot reach the website),  motivating the participants to configure the browser correctly, and providing the researchers with an indicator of successful censorship circumvention. While participants are on the computer, their screens will be recorded to capture how participants configure their browser, and to provide additional evidence that they have completed the tasks. The participants will be unaware that their screens are being recorded, to prevent deviations in behavior.

After completing the browsing tasks, we will administer a survey that 1) measures participant demographics, participant technical fluency, and participant familiarity with Tor and 2) collects qualitative feedback on from participants on their browsing experience, particularly with respect to any parts of the configuration interface which was confusing to them, but also about the browsing experience as a whole.  A rough draft of the survey can be found \href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.

 The experiment will conclude with a debriefing, which will inform that the participants of their screen capture and obtaining re-consent for the information.  \\
